Towards Transparency and Open Science

### 2023-02-06 manuscript.Rmd
passive

Having no access to the data when specifying the analysis forces the researcher to think about the process of induction.
They have to reason about all the possible data patterns they might encounter.
While this makes registration so difficult, it is exactly the information we need and from which we may derive the complexity of the inductive process.

>>>>

Having no access to the data when specifying the analysis forces the researcher to think about the process of induction.
They have to reason about all the possible data patterns they might encounter.
While this makes registration so difficult, it is exactly the information we need and from which the complexity of the inductive process might be derived.
